### 2021-05-17 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   experiments.tex   modified:   methodology.tex

@@

The first one, \emph{Non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
Regarding LEAM, a literal class label is required, which is available only in HWU64, CLINC150, BANKING77. 
Thus, for other two datasets, we have to use its class number instead. 
Empirically, a non-pretrained model based system are not performing as well as a pretrained models based in many NLP tasks.
Our listing these non-pretrained model based systems here is serving a comprehensive performance comparison on our datasets.

>>>>

\begin{table*}
  \begin{centering}
    \scalebox{0.75}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & Intent detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & Intent detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & Intent detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        FRAMES & Intent detection with NER & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
        \hline
        ATIS & Intent detection with NER & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

  \label{tbe:dataset statistic}
\end{table*}

@@

The first one, \emph{non-pretrained model based classification system}, which consists of a typical CNN based TextCNN \cite{kim2014convolutional}, and a label-embedding based LEAM \cite{wang2018joint}. 
Regarding TextCNN, the input is from RoBERTa tokenization, and the kernels are set as 1, 2, 3, 4, 5. 
Regarding LEAM, a literal class label is required, which is available only in HWU64, CLINC150, BANKING77. 
Thus, for other two datasets, we have to use its class number instead. 
Empirically, a non-pretrained model based system are not performing as well as a pretrained models based in many NLP tasks.
Our listing these non-pretrained model based systems here is serving a comprehensive performance comparison on our datasets.
